---
title: "Introduction to the atmospheric Package"
author: "Dan Kelley (https://orcid.org/0000-0001-7808-5911)"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_width: 7
    fig_height: 5
    dpi: 72
    dev.args: list(pointsize=11)
vignette: >
  %\VignetteIndexEntry{Introduction to the atmospheric Package}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  markdown:
    wrap: 72
---


```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

**Abstract.** This shows how to plot a recent atmospheric sounding at the
default location, Shearwater, Nova Scotia, Canada.


# Plot the most recent sounding for Shearwater, Nova Scotia, Canada.


This example uses a sample data file that is provided in the package, because
otherwise building the vignette can yield an error, if the server (Reference 1)
is unreachable or is too busy to return files.

```{r, echo = TRUE}
library(atmosphere)
dayOffsets <- seq(-2, -1)
soundingFile <- try(downloadAtmosphericSounding())
file <- system.file("extdata", "Shearwater_2024-07-11.txt.gz", package = "atmosphere")
par(mar = c(3, 3, 1, 1), mgp = c(2, 0.7, 0))
sounding <- readAtmosphericSounding(file)
```

# References

1. <https://weather.uwyo.edu/upperair/sounding.html>
2. <https://weather.uwyo.edu/cgi-bin/sounding?region=naconf&TYPE=TEXT%3ALIST&YEAR=2024&MONTH=07&FROM=1012&TO=1012&STNM=73110>
